GPU Virtualization in the Cloud (a mejorar el t\'itulo!!!)

### 2015-10-05 paper.tex
openstack section
Primera descripcion de AWS añadida

@@

\begin{figure}[!t]
  \centering
  \includegraphics[width=.9\linewidth]{images/UI-launch.pdf}
  \caption{Launching Instances and assigning GPUs}
  \label{fig:ui-launch}
\end{figure}

\begin{figure}[!t]
  \centering
  \includegraphics[width=.85\linewidth]{images/UI-rgpus.pdf}
  \caption{GPU Information Panel}
  \label{fig:ui-rgpus}
\end{figure}

>>>>

\subsection{Amazon Web Services}
\label{sec:aws}
AWS~\cite{aws} is a public cloud computing provider
and it is composed by several cloud services such as 
 cloud-based computation, storage and other func-
tionality that enables organizations and/or individuals to deploy
services and applications on an on-demand basis. 
These services, replace IT infrastructure for most companies, and provide agility and instant elasticity matching 
perfectly with their softwares requirements.

From the point of view of HPC, AWS offers high performance facilities including 
instances equiped with GPUs and high performance network interconnection which 
are common resources used in this research field.

@@

\begin{figure}[!t]
  \centering
  \includegraphics[width=.9\linewidth]{images/UI-launch.jpg}
  \caption{Launching Instances and assigning GPUs}
  \label{fig:ui-launch}
\end{figure}

\begin{figure}[!t]
  \centering
  \includegraphics[width=.85\linewidth]{images/UI-rgpus.jpg}
  \caption{GPU Information Panel}
  \label{fig:ui-rgpus}
\end{figure}
